\vspace{-2cm} The effects of transitions of power on the contents of municipal government websites

### 2017-11-26 paper/manuscript.tex
improvements to stm, hclust, and some other stuff
added fightinwords and stm to the new scheme of state-agnostic scripts

\subsubsection{Informative Dirichlet model}
Consequently we follow their recommendation to use the informative Dirichlet model they present in the paper \citep{Monroe2008}. This approach aims to account for the fact that some words naturally occur more than others by applying a Dirichlet prior based on the distribution of words in random text. Figure \ref{fightinwords} shows the top words for both Democrats and Republicans - and accomplishes, to some extent, the goal of \citep{Monroe2008} of banishing frequent words from this list and supplanting them by text with greater semantic, and in our case, partisan meaning. For Democrats, words related to public finances, such as 'fund', 'budget', or 'tax' are common - congruent with the party's greater willingness to raise and spend money publicly. Similarly, 'federal' 'funds' also appear among the Democratic top words. By contrast Republicans prefer to devote their attentions to purely local, and for the most part, logistic matters. 'Trees', 'water', 'street' and 'sign' appear on the list of Republican top words, suggesting that these mayors largely focus on city planning.

@@

%fightin words results
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Top democratic and Republican words (Indiana), according to the informed Dirichlet model of Monroe et al. (2008). Ordering is top to bottom for Democrats, and vice versa for Republicans.}
	\label{fightinwords}
	\includegraphics[width=\linewidth]{figures/fightinWords.png}
\end{figure}

@@

%Partisan top words - stm Indiana
\input{tables/stmTopWordsIN.tex} %\ref{tabSTMLA}

%Partisan top words - stm Louisiana
\input{tables/stmTopWordsLA.tex} %\ref{tabSTMLA}

>>>>

\subsubsection{Informative Dirichlet model}
Consequently we follow their recommendation to use the informative Dirichlet model they present in the paper \citep{Monroe2008}. This approach aims to account for the fact that some words naturally occur more than others by applying a Dirichlet prior based on the distribution of words in random text. Figure \ref{fightinwordsIN} shows the top words for both Democrats and Republicans - and accomplishes, to some extent, the goal of \citep{Monroe2008} of banishing frequent words from this list and supplanting them by text with greater semantic, and in our case, partisan meaning. For Democrats, words related to public finances, such as 'fund', 'budget', or 'tax' are common - congruent with the party's greater willingness to raise and spend money publicly. Similarly, 'federal' 'funds' also appear among the Democratic top words. By contrast Republicans prefer to devote their attentions to purely local, and for the most part, logistic matters. 'Trees', 'water', 'street' and 'sign' appear on the list of Republican top words, suggesting that these mayors largely focus on city planning.

@@

%fightin words results
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Top democratic and Republican words (Indiana), according to the informed Dirichlet model of Monroe et al. (2008). Ordering is top to bottom for Democrats, and vice versa for Republicans.}
	\label{fightinwordsIN}
	\includegraphics[width=\linewidth]{figures/fightinWordsIN.png}
\end{figure}

@@

%Partisan top words - stm Indiana
%\input{tables/stmTopWordsIN.tex} %\ref{tabSTMLA}

%Partisan top words - stm Louisiana
%\input{tables/stmTopWordsLA.tex} %\ref{tabSTMLA}

%Partisan top words - stm Louisiana -- Rep
\input{tables/stmTopWordsINRep.tex} %\ref{tabSTMINRep}

%Partisan top words - stm Louisiana -- Dem
\input{tables/stmTopWordsINDem.tex} %\ref{tabSTMLADem}

%Partisan top words - stm Louisiana -- Rep
\input{tables/stmTopWordsLARep.tex} %\ref{tabSTMLARep}

%Partisan top words - stm Louisiana -- Dem
\input{tables/stmTopWordsLADem.tex} %\ref{tabSTMLADem}
